\sys: Light-touch Data-Parallel Shell Processing

### 2020-05-24 pldi/draft.tex
Update takeaway

\heading{Take-aways}
\sys can be applied to programs of significant size and input
%% \todo{larger} % real/realistic? implies that prior benchmarks were not  
%% programs
%% with modern input sides
to offer significant acceleration.
A broader %% and more-ambitious
take-away is that \sys is able to exploit the until now unharnessed parallelization opportunities of inter-program scripts that are used widely to download, extract, and clean data.

untapped potential 
that is 
exploitble

does not fall within purely compute-intensive targets that are the focus of conventional parallelization techniques.

>>>>

\heading{Take-aways}
\sys can be applied to programs of significant size and input
%% \todo{larger} % real/realistic? implies that prior benchmarks were not  
%% programs
%% with modern input sides
to offer significant acceleration.
A broader take-away is that \sys is able to extract parallelism from fragments that do not fall under purely compute-intensive regions that are the focus of conventional parallelization systems.
